Modern Graph Generators: A Survey

### 2018-11-09 classification.tex
rewriting Part I

\begin{itemize}
  \item \emph{Degree-based generators}: Given a degree distribution (typically following a power law), these generators (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.).
  \item \emph{Procedural generators}: These generators (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.
\end{itemize}

>>>>

\begin{itemize}
  \item \emph{Degree-based generators}: Given a (customarily power law) degree distribution, these generators (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) attempt to produce a graph matching the above distribution. However, they do not provide any insights about the graph or ignore the matching of other parameters such as for instance small diameter, eigenvalues and so on.
  \item \emph{Procedural generators}: These generators (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.
\end{itemize}

### 2018-11-09 introduction.tex
rewriting Part I

Aggarwal and Subbian \cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on
Densification Power Law (DPL) and shrinking diameters and community-guided
attachment properties \cite{Leskovec:2005:GOT:1081870.1081893} is then considered, along with tackling Kronecker
recursion with recursive tensor multiplication \cite{AkogluMF08}.
We refer the reader to this survey for evolutionary network generators and
we further discuss the open challenges of evolving graph data in Section 5.
%\TODO{Better highlight the differences when Sherif's part is in.}

>>>>

Aggarwal and Subbian \cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on
Densification Power Law (DPL) and shrinking diameters and community-guided
attachment properties \cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of networks tackling Kronecker
recursion with recursive tensor multiplication \cite{AkogluMF08} is then considered in the above survey.
We refer the reader to the aformentioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
%\TODO{Better highlight the differences when Sherif's part is in.}
